Giant Low Surface Brightness Galaxies As Merger Remnants

### 2015-04-16 glsb.tex
discussion outline

\section{Star Formation Histories}
Following the work in \citet{Yoachim10,Yoachim12}, we generate a suite of model galaxy SEDs using relatively simple star formation histories and find the best fitting single model.  We break the star formation history into three age bins, 0-10 Gyr, 10-11.5 Gyr, and 11.5-12 Gyr.  We assume each age bin has a constant star formation with a level of 0, 0.5, 1, or 10 solar-masses per year.  Each SFH can have a metallicity of [Z/H] = -2.3,-1.70,-0.70, -0.40, 0.0, or  0.40.  We do not include any metallicity evolution, as all the age bins in a given model has the same metallicity.  This gives us 361 unique non-zero model spectra.

@@

@@

Our initial long slit observations don't really show much as far as correlation between the bulge and disk rotation vectors.  We are currently proposing for higher resolution observations that will make it possible to measure the stellar kinematics of the central object in detail to see if it is a relatively undisturbed elliptical.

@@

Should probably figure out if these things are fast or slow rotators by the \citet{Emsell11} definition.  Also see \citet{Capp11} that says slow rotators are very rare in the field.  So it might be strange if Malin 2 and UGC 6614 are slow rotators...

>>>>

\section{Star Formation Histories}

Following the work in \citet{Yoachim10,Yoachim12}, we generate a suite of model galaxy SEDs using relatively simple star formation histories and find the best fitting single model.  We break the star formation history into three age bins, 0-10 Gyr, 10-11.5 Gyr, and 11.5-12 Gyr.  We assume each age bin has a constant star formation with a level of 0, 0.5, 1, or 10 solar-masses per year.  Each SFH can have a metallicity of [Z/H] = -2.3,-1.70,-0.70, -0.40, 0.0, or  0.40.  We do not include any metallicity evolution, as all the age bins in a given model has the same metallicity.  This gives us 361 unique non-zero model spectra.

@@

Outline for discussion section
\begin{itemize}
\item{We find the GLSB systems Malin~2 and UGC~6614 are observationally most consistent with being normal elliptical galaxies that have undergone a high angular momentum minor merger with a gas rich system.}
\item{recap photometric evidence--the centers look just like SDSS ellipticals.}
\item{recap star formation histories. Disk is dominated by old stars.}
\item{Discuss metallicity gradient. Hard to imagine how such a metal poor disk could form right next to a very metal rich core.}
\item{extended comparison to \citet{Kasparova14}}
  \begin{itemize}
    \item{Mass model of Malin~2 requires a huge isothermal core radius.}
    \item{They measure gas metallicities and find solar in the center and half-solar at 20-30 kpc.  While it is a fool's errand to compare metallicities between stars and gas, it is interesting that the gas metallicity gradient is much smaller than in the stars.  If the central stellar metallicity is indeed super-solar and the gas metallicity only solar, that implies there must have been low-metallicity gas accretion onto the system at some point.  Hmm, looking at DR12 stuff, the pipeline reducitons are fitting solar metallicity to the center, not sure I believe that.  }
      \item{They have a nice mass-model that becomes dark matter dominated at around r=20 kpc.  Could this be the normal shape of elliptical dark matter halos?}
  \end{itemize}

\item{This could be the strongest evidence for very massive elliptical dark matter halos. }
  \item{plan on getting higher spatial resolution spectra of the centers to confirm they are typical elliptical galaxies.}
\end{itemize}

@@

%Our initial long slit observations don't really show much as far as correlation between the bulge and disk rotation vectors.  We are currently proposing for higher resolution observations that will make it possible to measure the stellar kinematics of the central object in detail to see if it is a relatively undisturbed elliptical.

@@

Should probably figure out if these things are fast or slow rotators by the \citet{Emsell11} definition.  Also see \citet{Capp11} that says slow rotators are very rare in the field.  So it might be strange if Malin 2 and UGC 6614 are slow rotators.
